Case Study (McKenna)

### 2020-06-17 Cases/mrp/Case Study (McKenna) .Rmd
Reorganizing case study and files.

## Postratification

Postratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people

$$\omega=\displaystyle\frac{$$\sum_{j=1}^{J}\beta_{j}*N_{j}$$}{$$\sum_{j=1}^{J}N_{j}$$}$$
Postratification can be performed in stan using the generated quantities block.

@@

## Compare to Population 
Because we are using simulated data we can see how our poststratified predictions compare to the true population

>>>>

## Post-Stratification

Post-stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people

$$\omega=\displaystyle\frac{$$\sum_{j=1}^{J}\beta_{j}*N_{j}$$}{$$\sum_{j=1}^{J}N_{j}$$}$$
Post-stratification can be performed in stan using the generated quantities block.

@@

## Compare to Population

Because we are using simulated data we can see how our poststratified predictions compare to the true population.
